---
title: "MultiSpecies Analysis"
author: "Elizabeth Hiroyasu"
date: "May 1, 2017"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
library(devtools)
library(roxygen2)
load_all("DemTrend")
library(DemographicTrend)

library(tidyverse)
```

##Detecting Trends in Populations
Using the Compadre database (www.compadre-db.org), we are examining if demographic population vital rates can be used to detect trends in a population.

The simulations run here are focused on herbaceous, unmanipulated plant populations with a minimum of 3 demographic stages and at least six years of data. First we read the data in from the Compadre database and filter it using the Load_Compadre_Data function in the DemographicTrend package. 
```{r}
CompadreFile <- "COMPADRE_v.4.0.1.Rdata"
mydata <- Load_Compadre_Data(CompadreFile)
pop_list <- unique(cbind(mydata$metadata$SpeciesAuthor,mydata$metadata$MatrixPopulation))
```

##Simulating the population
We can insert a small trend in the population (delta), then measure how easily we can detect this trend over time.
```{r}
#num_pops <- dim(pop_list)[1] #actual
num_pops <- 5 # for debugging
delta=0.001
alpha=seq(from=0.01, to=0.2, by=delta)

output <- list(NULL)

for (k in 1:num_pops) {
  print(k)
  temp1<-subset(mydata$metadata, SpeciesAuthor==pop_list[k,1] & MatrixPopulation==pop_list[k,2])
  
  MatrixData<- as.array(mydata$mat[mydata$metadata$SpeciesAuthor==pop_list[k,1] & mydata$metadata$MatrixPopulation==pop_list[k,2]])
  
  save<-as.numeric(rownames(temp1))
  MatClass<-mydata$mat_class[save]
  
  active_stages<-subset(MatClass[[1]]$MatrixClassNumber, MatClass[[1]]$MatrixClassOrganized=='active')
  #extracting matrices:
  temp<- extract_mat(MatrixData)
  surv_mat<-temp$surv_mat
  fert_mat<-temp$fert_mat
  clon_mat<-temp$clon_mat
  trans_mat<-temp$trans_mat
  
  # Remove all-zero years, as that causes problems
  all_zero <- apply(trans_mat, 3, mean) == 0
  surv_mat <- surv_mat[,,!all_zero]
  fert_mat <- fert_mat[,,!all_zero]
  clon_mat <- clon_mat[,,!all_zero]
  trans_mat <- trans_mat[,,!all_zero]
  
  # The following populations have really strange matrices: 68
  # # The following matrices have some years of zero survival and others of zero fertility: 212
   if(length(dim(trans_mat)) > 2){
   if (mean(fert_mat) > 0 & k != 68 & k != 212 & dim(trans_mat)[3] >= 5 & max(temp1$SurvivalIssue) <= 1) {
  #calculating the number of stages in the matrix:
  nstage<-1:dim(surv_mat)[1]
  
  #calculating the mean transition matrices and eigenvalues
  mean_trans_mat<-apply(trans_mat, c(1,2), mean)
  eigenvalues<-eigen(mean_trans_mat)

  #Running simulations
  return_pv<-replicate(10, calc_pv(surv_mat, fert_mat, trans_mat, nstage=nstage, years=1:10, stage2mod=active_stages, beta=0.0, active_stages = active_stages, verbose=FALSE))


  #Analysis
  output[[k]]<-analyze_pv(alpha, return_pv)
  output[[k]]<-c(output[[k]], names=list(pop_list[k,]), eigenvalues=eigenvalues)

  }
  }
  
}
```

