---
title: "CiPi_Analysis"
author: "Elizabeth Hiroyasu"
date: "Wednesday, May 06, 2015"
output: html_document
---

This is a sample analysis using the demographic trend package for a population of Cirsium pitcheri.

# Data loading
## Load in the Compadre data and take the default selection
The data file needs to be in the working directory. It can be downloaded from http://www.compadre-db.org.


```{r}
library(DemographicTrend)
CompadreFile <- "COMPADRE_10_11_2014_version_3.0.Rdata"
mydata <- Load_Compadre_Data(CompadreFile)
```

#Subsetting out the cipi dataset
CiPi <- subset(mydata$metadata, Population =="CiPi 1")

#pulling out CiPi Matrices
save<-as.numeric(rownames(CiPi))
CiPiMat<- as.array(compadre$mat[save])

##pulling out cipi survival matrices
surv_mat <- array(unlist(CiPiMat), dim = c(nrow(CiPiMat[[1]]$matU), ncol(CiPiMat[[1]]$matU), length(CiPiMat)))

##pulling out cipi reproduction
fert_mat <- array(unlist(CiPiMat), dim = c(nrow(CiPiMat[[1]]$matF), ncol(CiPiMat[[1]]$matF), length(CiPiMat)))

##pulling out cipi transition matrices
trans <- array(unlist(CiPiMat), dim = c(nrow(CiPiMat[[1]]$matA), ncol(CiPiMat[[1]]$matA), length(CiPiMat)))


##Loading the N0 vectors:
##subsetting the data for cipi data
N0_data <- load_N0()
cipi_nx<- subset(N0_data, POP =="CIPI_1")
nx_str<- cipi_nx$Nx
years <- 1:length(cipi_nx$YR)
N0_data<-nx_out(nx_str)

To introduce simulations to compare p-values using the functions in the Demographic Trend Package:
```{r}
return_pv<-replicate(10, trend_sim())
```
This code can be adjusted to increase the number of replications and returns a list of p-values for the survival and abundance regressions.