---
title: "Test analyses"
author: "Bruce Kendall"
date: "May 5, 2015"
output: html_document
---

Here we work out the methods for doing the demographic trend analyses.

# Data loading and munging
## Load in the Compadre data and take the default selection
The data file needs to be in the working directory. It can be downloaded from http://www.compadre-db.org.
```{r LoadData}
library(DemographicTrend)
CompadreFile <- "COMPADRE_10_11_2014_version_3.0.Rdata"
mydata <- Load_Compadre_Data(CompadreFile)
```

## Find a dataset to work with
The first population has a corrupted `matF`:
```{r}
mydata$mat[1]
```
Presumably this is something to do with the automatic decomopsition failing to deal with multiple rows of reproduction. Let's get rid of the this population.
```{r}
BadAuthors <- mydata$metadata$Authors[1]

# Need to write a function to do this, but have to figure out how to parse the condition
    metadata<- subset(mydata$metadata)

  ##then refine by specified components
  tempMetadata <- subset(metadata, Authors != BadAuthors)
  tempMat <- mydata$mat[mydata$metadata$Authors != BadAuthors]

  mydata <- list(metadata=tempMetadata, mat=tempMat)
rm(tempMetadata); rm(tempMat)

mydata$mat[1]
```

Select the annual matrices from this first species/population.
